A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition

### 2016-10-21 paper.tex
update

Firstly, the average fitness value over 100 generations is calculated by the average best fitness so far found per generation over 30 independent runs. The marked value plotted in the first group of the figure ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness value between generation 0 and generation 15-25, the remained generation continues to perform a very slight improvement in the fitness value and reach a plateau with no further changes. Furthermore, it is a common feature in three tasks’ average fitness graph. Also, there is a fast convergence of the population can be observed. That is simply because of many repetitive solutions as the indirect web service composition representation, although it is a large search space.

We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third groups in Figure \ref{exp_fitnessvalue}.  In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found,  and further calculated their mean over 30 independent runs respectively. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend. However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent, yet the combination of all the influential functional quality part evolved towards an optimised solution.

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation. We construct the results in the fourth groups in Figure \ref{exp_fitnessvalue}. It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on. Luckily, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an uncomplicated example of the web service composition solution to problem1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated the all the non-functional attributes of $V$ using aggregation rules defined before.

After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for solution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is. In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding solutions. In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method. From the table below.

>>>>

Firstly, the average fitness value over 100 generations is calculated by the average best fitness so far found per generation over 30 independent runs. The value plotted in the first column group of figure \ref{exp_fitnessvalue} ranges from 0 to 1, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. Also, there is a fast convergence of the fitness value can be observed. That is simply because of many repetitive solutions as the indirect web service composition representation in a large search space.

We also investigate the variation in functional quality part including two sub factors --- average matchType quality and average similarity quality from generation 0 to 99 in second and third column groups in Figure \ref{exp_fitnessvalue}. In these groups,  both the average matchType quality and average similarity quality are the average value corresponding to the average best fitness so far found plotted in the first column group,  and further calculated their mean over 30 independent runs respectively. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend. However, there are some slight fluctuations over the generations, and it could be reasonably treated as a typical situation that theoretically single objective function prevents selecting the lowest semantic matchmaking quality without granting for the excellent.

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation. We construct the results in the fourth column group in Figure \ref{exp_fitnessvalue}. It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks. Additionally, QoS (avg) with optimum have evolved towards an overall excellent state, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before.This standard solution model helps us to make better comparison for evaluating the results from different approaches.

After a well-defined solution is discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using  black-box testing for solution comparison, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is. In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering five different conditions (five independent tasks) associated with three corresponding solutions. In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method. From the table below.
